Under-ice acoustic navigation using real-time model-aided range estimation

### 2022-03-31 manuscript/manuscript.tex
abstract < 200 words

\begin{abstract}
The long baseline (LBL) underwater navigation paradigm relies on the conversion of travel times into pseudoranges to trilaterate position. 
For real-time autonomous underwater vehicle (AUV) operations, this conversion assumes an isovelocity sound speed.
For re-navigation, computationally and/or labor intensive acoustic modeling may be employed to reduce uncertainty.
This work demonstrates a real-time ray-based prediction method of the effective sound speed along a path from source to receiver to minimize pseudorange error.
\llabel{2.1} This method was implemented for an AUV-LBL system in the Beaufort Sea, in total ice-covered conditions and a double-ducted propagation environment.
\llabel{2.2} Given the lack of Global Navigation Satellite System (GNSS) data throughout the vehicle's mission, the pseudorange performance is first evaluated on acoustic transmissions between GNSS-linked beacons.
The mean real-time absolute range error between beacons is roughly 11 m at distances up to 3 km.
A consistent overestimation in the real-time method provides insights for improved eigenray filtering by the number of bounces.
An operationally equivalent pipeline is used to re-position the LBL beacons and re-navigate the AUV, using modeled, historical, and locally observed sound speed profiles.
The best re-navigation error is 1.84 $\pm$ 2.19 m rms.
\llabel{2.3} The improved performance suggests this approach extends the single meter accuracy of the deployed GNSS units into the water column.
\end{abstract}

>>>>

\begin{abstract}
The long baseline (LBL) underwater navigation paradigm relies on the conversion of travel times into pseudoranges to trilaterate position. 
For real-time autonomous underwater vehicle (AUV) operations, this conversion assumes an isovelocity sound speed.
For re-navigation, computationally and/or labor-intensive acoustic modeling may be employed to reduce uncertainty.
This work demonstrates a real-time ray-based prediction of the effective sound speed along a path from source to receiver.
\llabel{2.1} This method was implemented for an AUV-LBL system in the Beaufort Sea, in an ice-covered and a double-ducted propagation environment.
\llabel{2.2} Given the lack of Global Navigation Satellite System (GNSS) data throughout the vehicle's mission, the pseudorange performance is first evaluated on acoustic transmissions between GNSS-linked beacons.
The mean real-time absolute range error between beacons is roughly 11 m at distances up to 3 km.
A consistent overestimation in the real-time method provides insights for improved eigenray filtering by the number of bounces.
An operationally equivalent pipeline is used to re-position the LBL beacons and re-navigate the AUV, using modeled, historical, and locally observed sound speed profiles.
The best re-navigation error is 1.84 $\pm$ 2.19 m rms.
\llabel{2.3} The improved performance suggests this approach extends the single meter accuracy of the deployed GNSS units into the water column.
\end{abstract}
